WIDS 2024 Final Presentation

### 2024-01-12 Documents/Presentation.qmd
fixed third question
added biblgiography

1.  Is there any relationship between collective bargaining rates among workers to house delegation makeup?
2.  Is there any relationship between collective bargaining rates among workers and wages
3.  Is there any relationship between collective bargaining rates among workers and wages?

@@

>>>>

1.  Is there any relationship between collective bargaining rates among workers to house delegation makeup?
2.  Is there any relationship between collective bargaining rates among workers and wages?
3.  Do collective bargaining rates effect wealth inequality?

@@

"Johnthegeek". 2021. “Wealth and income over time.” GitHub. https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-02-09/readme.md.

"Johnthegeek". 2023. “Union Membership in the United States.” GitHub. https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-09-05/readme.md.

"Johnthegeek". 2023. “US House Election Results.” GitHub. https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-11-07/readme.md.

"LisleJoem". 2021. “US Minimum Wage by State from 1968 to 2020 and 2020 Equivalent Dollars.” Kaggle. https://www.kaggle.com/datasets/lislejoem/us-minimum-wage-by-state-from-1968-to-2017.
